### 2024-05-22 getting-started.qmd
20240521 - add data from nflfastR

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install several key `R` packages:
```{r}
#| eval: false

@@

>>>>

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install several key `R` packages:

@@

For instance, you can use the following code to install the `nflfastR` package:

install.packages("nflfastR")
```

## Load Packages {#sec-loadPackages}

```{r}
library("nflfastR")
library("tidyverse")
```

## Download Football Data {#sec-downloadFootballData}

### Play-By-Play Data {#sec-downloadPlayByPlay}

To download play-by-play data from prior weeks and seasons, we can use the `load_pbp()` function of the `nflfastR` package:

nfl_pbp <- nflfastR::load_pbp(seasons = TRUE)
```

```{r}
#| eval: false
#| include: false

library("here")

save(
  nfl_pbp,
  file = here("data", "nfl_pbp.RData")
)
```

```{r}
#| include: false

library("here")

load(file = here("data", "nfl_pbp.RData"))
```

### Player Info {#sec-downloadPlayerInfo}

## Calculations {#sec-calculations}

### Historical Actual Player Statistics {#sec-calculateActualStats}

TODO: compute player stats for defenses (`calculate_player_stats_def()`) and kickers (`calculate_player_stats_kicking()`).

Note: The following code takes a while to run.

First, subset the data by year:

nfl_pbp_1999 <- nfl_pbp %>% filter(season == 1999)
nfl_pbp_2000 <- nfl_pbp %>% filter(season == 2000)
nfl_pbp_2001 <- nfl_pbp %>% filter(season == 2001)
nfl_pbp_2002 <- nfl_pbp %>% filter(season == 2002)
nfl_pbp_2003 <- nfl_pbp %>% filter(season == 2003)
nfl_pbp_2004 <- nfl_pbp %>% filter(season == 2004)
nfl_pbp_2005 <- nfl_pbp %>% filter(season == 2005)
nfl_pbp_2006 <- nfl_pbp %>% filter(season == 2006)
nfl_pbp_2007 <- nfl_pbp %>% filter(season == 2007)
nfl_pbp_2008 <- nfl_pbp %>% filter(season == 2008)
nfl_pbp_2009 <- nfl_pbp %>% filter(season == 2009)
nfl_pbp_2010 <- nfl_pbp %>% filter(season == 2010)
nfl_pbp_2011 <- nfl_pbp %>% filter(season == 2011)
nfl_pbp_2012 <- nfl_pbp %>% filter(season == 2012)
nfl_pbp_2013 <- nfl_pbp %>% filter(season == 2013)
nfl_pbp_2014 <- nfl_pbp %>% filter(season == 2014)
nfl_pbp_2015 <- nfl_pbp %>% filter(season == 2015)
nfl_pbp_2016 <- nfl_pbp %>% filter(season == 2016)
nfl_pbp_2017 <- nfl_pbp %>% filter(season == 2017)
nfl_pbp_2018 <- nfl_pbp %>% filter(season == 2018)
nfl_pbp_2019 <- nfl_pbp %>% filter(season == 2019)
nfl_pbp_2020 <- nfl_pbp %>% filter(season == 2020)
nfl_pbp_2021 <- nfl_pbp %>% filter(season == 2021)
nfl_pbp_2022 <- nfl_pbp %>% filter(season == 2022)
nfl_pbp_2023 <- nfl_pbp %>% filter(season == 2023)
```

Second, compute the weekly stats:

nfl_actualStats_weekly <- nflfastR::calculate_player_stats(
  nfl_pbp,
  weekly = TRUE)
```

```{r}
#| eval: false
#| include: false

save(
  nfl_actualStats_weekly,
  file = here("data", "nfl_actualStats_weekly.RData")
)
```

Third, compute the career stats:

nfl_actualStats_career <- nflfastR::calculate_player_stats(
  nfl_pbp,
  weekly = FALSE)
```

```{r}
#| eval: false
#| include: false

save(
  nfl_actualStats_career,
  file = here("data", "nfl_actualStats_career.RData")
)
```

Fourth, compute seasonal stats by year:

nfl_actualStats_seasonal_1999 <- nflfastR::calculate_player_stats(
  nfl_pbp_1999,
  weekly = FALSE)

nfl_actualStats_seasonal_2000 <- nflfastR::calculate_player_stats(
  nfl_pbp_2000,
  weekly = FALSE)

nfl_actualStats_seasonal_2001 <- nflfastR::calculate_player_stats(
  nfl_pbp_2001,
  weekly = FALSE)

nfl_actualStats_seasonal_2002 <- nflfastR::calculate_player_stats(
  nfl_pbp_2002,
  weekly = FALSE)

nfl_actualStats_seasonal_2003 <- nflfastR::calculate_player_stats(
  nfl_pbp_2003,
  weekly = FALSE)

nfl_actualStats_seasonal_2004 <- nflfastR::calculate_player_stats(
  nfl_pbp_2004,
  weekly = FALSE)

nfl_actualStats_seasonal_2005 <- nflfastR::calculate_player_stats(
  nfl_pbp_2005,
  weekly = FALSE)

nfl_actualStats_seasonal_2006 <- nflfastR::calculate_player_stats(
  nfl_pbp_2006,
  weekly = FALSE)

nfl_actualStats_seasonal_2007 <- nflfastR::calculate_player_stats(
  nfl_pbp_2007,
  weekly = FALSE)

nfl_actualStats_seasonal_2008 <- nflfastR::calculate_player_stats(
  nfl_pbp_2008,
  weekly = FALSE)

nfl_actualStats_seasonal_2009 <- nflfastR::calculate_player_stats(
  nfl_pbp_2009,
  weekly = FALSE)

nfl_actualStats_seasonal_2010 <- nflfastR::calculate_player_stats(
  nfl_pbp_2010,
  weekly = FALSE)

nfl_actualStats_seasonal_2011 <- nflfastR::calculate_player_stats(
  nfl_pbp_2011,
  weekly = FALSE)

nfl_actualStats_seasonal_2012 <- nflfastR::calculate_player_stats(
  nfl_pbp_2012,
  weekly = FALSE)

nfl_actualStats_seasonal_2013 <- nflfastR::calculate_player_stats(
  nfl_pbp_2013,
  weekly = FALSE)

nfl_actualStats_seasonal_2014 <- nflfastR::calculate_player_stats(
  nfl_pbp_2014,
  weekly = FALSE)

nfl_actualStats_seasonal_2015 <- nflfastR::calculate_player_stats(
  nfl_pbp_2015,
  weekly = FALSE)

nfl_actualStats_seasonal_2016 <- nflfastR::calculate_player_stats(
  nfl_pbp_2016,
  weekly = FALSE)

nfl_actualStats_seasonal_2017 <- nflfastR::calculate_player_stats(
  nfl_pbp_2017,
  weekly = FALSE)

nfl_actualStats_seasonal_2018 <- nflfastR::calculate_player_stats(
  nfl_pbp_2018,
  weekly = FALSE)

nfl_actualStats_seasonal_2019 <- nflfastR::calculate_player_stats(
  nfl_pbp_2019,
  weekly = FALSE)

nfl_actualStats_seasonal_2020 <- nflfastR::calculate_player_stats(
  nfl_pbp_2020,
  weekly = FALSE)

nfl_actualStats_seasonal_2021 <- nflfastR::calculate_player_stats(
  nfl_pbp_2021,
  weekly = FALSE)

nfl_actualStats_seasonal_2022 <- nflfastR::calculate_player_stats(
  nfl_pbp_2022,
  weekly = FALSE)

nfl_actualStats_seasonal_2023 <- nflfastR::calculate_player_stats(
  nfl_pbp_2023,
  weekly = FALSE)

nfl_actualStats_seasonal <- bind_rows(
  nfl_actualStats_seasonal_1999,
  nfl_actualStats_seasonal_2000,
  nfl_actualStats_seasonal_2001,
  nfl_actualStats_seasonal_2002,
  nfl_actualStats_seasonal_2003,
  nfl_actualStats_seasonal_2004,
  nfl_actualStats_seasonal_2005,
  nfl_actualStats_seasonal_2006,
  nfl_actualStats_seasonal_2007,
  nfl_actualStats_seasonal_2008,
  nfl_actualStats_seasonal_2009,
  nfl_actualStats_seasonal_2010,
  nfl_actualStats_seasonal_2011,
  nfl_actualStats_seasonal_2012,
  nfl_actualStats_seasonal_2013,
  nfl_actualStats_seasonal_2014,
  nfl_actualStats_seasonal_2015,
  nfl_actualStats_seasonal_2016,
  nfl_actualStats_seasonal_2017,
  nfl_actualStats_seasonal_2018,
  nfl_actualStats_seasonal_2019,
  nfl_actualStats_seasonal_2020,
  nfl_actualStats_seasonal_2021,
  nfl_actualStats_seasonal_2022,
  nfl_actualStats_seasonal_2023,
  .id = "id"
)

nfl_actualStats_seasonal$season <- NA

nfl_actualStats_seasonal$id <- as.integer(nfl_actualStats_seasonal$id)

for(i in 1:max(nfl_actualStats_seasonal$id)){
  nfl_actualStats_seasonal$season[which(nfl_actualStats_seasonal$id == i)] <- 1998 + i
}
```

```{r}
#| eval: false
#| include: false

save(
  nfl_actualStats_seasonal,
  file = here("data", "nfl_actualStats_seasonal.RData")
)
```

### Historical Actual Fantasy Points {#sec-calculateActualPoints}
